Kit Theory

### 2023-06-20 paper/paper.tex
Update.
Paper: added references and renamed Mode to Sort.

\documentclass[sigplan, screen]{acmart}
% \documentclass[sigplan, screen, anonymous, review, authordraft]{acmart}

@@

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

@@

\usepackage{newunicodechar}
\newunicodechar{≡}{\ensuremath{\equiv}}
\newunicodechar{ℕ}{\ensuremath{\mathbb{N}}}
\newunicodechar{∘}{\ensuremath{\circ}}
\newunicodechar{∅}{\ensuremath{\varnothing}}
\newunicodechar{⇒}{\ensuremath{\Rightarrow}}
\newunicodechar{∋}{\ensuremath{\ni}}
\newunicodechar{∷}{\ensuremath{\mathop{::}}}
\newunicodechar{⊢}{\ensuremath{\vdash}}
\newunicodechar{∀}{\ensuremath{\forall}}
\newunicodechar{₁}{\ensuremath{{}_1}}
\newunicodechar{₂}{\ensuremath{{}_2}}
\newunicodechar{ᵣ}{\ensuremath{{}_{\textsf{r}}}}
\newunicodechar{ₛ}{\ensuremath{{}_{\textsf{s}}}}
\newunicodechar{→}{\ensuremath{\to}}
\newunicodechar{◆}{\ensuremath{\diamond}}
% \newunicodechar{Γ}{\ensuremath{\texttt{\Gamma}}}
% \newunicodechar{λ}{\ensuremath{\texttt{\lambda}}}

% \usepackage{cite}
% \usepackage{DejaVuSansMono}
\usepackage{alphabeta} % Make greek letter macros also work in text-mode.

@@

>>>>

% \documentclass[sigplan, screen]{acmart}
% \documentclass[sigplan, screen, anonymous, review, authordraft]{acmart}
% \documentclass[sigplan,10pt,anonymous,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\documentclass[sigplan,10pt]{acmart}

@@

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stmaryrd}

@@

\usepackage{bbold} % lower case mathbb letters

\usepackage{agda-unicode}

% \usepackage{cite}
% \usepackage{DejaVuSansMono}
% \usepackage{alphabeta} % Make greek letter macros also work in text-mode.

@@

  \section{Introduction}
  \newpage

  \section{Syntax}
  \subsection{Library}
  \KVariables
  \KSortTy
  \KTerms
  \subsection{System F}
  \FSort
  \FSyntax
  \FTerms

  \section{Maps}
  \subsection{Library}
  \KKit
  \KMap
  \KAp
  \KExt
  \KLift
  \KId
  \KSingle
  \KWeaken
  \KEq
  \KFunExt
  \KIdLift
  % \KIdLiftProof
  \KKitNotation
  \KTraversal
  \KKitInstances
  \KKitOpen
  \subsection{System F}
  \FTraversalOp
  \FTraversalId
  \FTraversalIdProofInteresting
  % \FTraversalIdProofRest
  \FTraversal

  \section{Map Composition}
  \subsection{Library}
  \KWkKit
  \KWkKitInstances
  \KComposeKit
  \KComposition
  \KComposeKitAp
  % \KComposeKitApProof
  \KDistLiftCompose
  % \KDistLiftComposeProof
  \KComposeKitNotation
  \KComposeTraversal
  \KCommLiftWeaken
  % \KCommLiftWeakenProof
  \KCommLiftWeakenTraverse
  % \KCommLiftWeakenTraverseProof
  \KComposeKitInstances
  \KComposeKitInstancesConcrete
  \KWeakenCancelsSingle
  % \KWeakenCancelsSingleProof
  \KWeakenCancelsSingleTraverse
  % \KWeakenCancelsSingleTraverseProof
  \KDistLiftSingle
  % \KDistLiftSingleProof
  \KDistLiftSingleTraverse
  % \KDistLiftSingleTraverseProof
  \subsection{System F}
  \FAssoc
  \FAssocProofInteresting
  % \FAssocProofRest
  \FComposeTraversal

  \section{Types \& Contexts}
  \subsection{Library}
  \KTypeSorts
  \KTypes
  \KContextHelper
  \KContexts
  \KContextLookup
  \subsection{System F}
  \FTypes

  \section{Typing}
  \subsection{Library}
  \KVariableTyping
  \KTyping
  \KTypingKit
  \KMapTyping
  \KLiftTyping
  % \KLiftTypingProof
  \KSingleTyping
  % \KSingleTypingProof
  \KTypingNotation
  \KTypingTraversal
  \KTypingInstances
  % \KTypingTraversalNotation
  \subsection{System F}
  \FTyping
  \FTypingInst
  \FPreserve
  \FTypingTraversal

  \section{Semantics}
  % \FValues
  \FReduction

  \section{Subject Reduction}
  \FSubjectReduction
  \FSubjectReductionProofInteresting
  % \FSubjectReductionProofRest

  \section{Related Work}
  Autosubst \cite{DBLP:conf/cpp/StarkSK19, DBLP:conf/itp/SchaferTS15}.
  Kits \cite{DBLP:journals/jar/BentonHKM12, unpublished:mcbride2005kits}.
  Kits linear \cite{DBLP:journals/corr/abs-2005-02247}.
  Universe \cite{DBLP:journals/pacmpl/AllaisA0MM18}.
